\documentclass{article}
\title{Research Facebook API's}
\begin{document}
\section{Overview}
Facebook for developers is divided up into plaforms.
Each of those platforms have their own API('s).
The platforms are Social Plugins, Facebook Login, Open Graph, Facebook API's, Games, Media, Payments, App Center, Promote Your App, iOS and Andriod.
\section{Social Plugins}
Social plugins let you see what your friends have liked, commented on or shared on sites across the web.(Not usefull) 
\section{Facebook login}
This API makes it possible to use your facebook details to automaticly register for
a given website.(Could be usefull but not really)
\section{Open Graph}
The Open Graph lets apps tell stories on Facebook through a structured, strongly typed API.People use stories to share the things they're doing, the people they're doing them with and the places where they happen. Not usefull so futher details was left out.
\section{Facebook API's}
\subsection{Graph API}
It can search for posts ,pictures, the amount of likes and places.
It can search for places in a certian area. Posts can not besearch by a given
area, although they can contain the location they were post at.
\subsection{Facebook Query Language FQL}
Is build on top of the graph API but works more like Structured Query Langauge.
It has the same fuctionality as the Graph API but results from one query can be used in another query. 
It can search for posts by a certain area but the follow must hold
\begin{itemize}
\item you were tagged in the Post
\item a friend was tagged in the Post
\item you authored the Post
\item a friend authored the Post
\end{itemize}
And they have the location information.
\subsection{Internationalization}
Is a translation framework.
\section{Payments}
Facebook Payments gives you a safe and easy way to enable people to pay for digital items in your game.
\end{document}
