\documentclass{article}
\author{J.\,J.\,Martin}
\title{Basic UI \\investigation}
\begin{document}
\maketitle

\section{Introduction}
For our project we are investigating HTML 5 and JQuery, for implementing a basic user interface.
\section{Hyper Text Markup Language 5}
HTML is a language for specifying the layout of websites, which we will be using to create our website . HTML works on a basis of ``tags'' which are used to define ``environments''. The format of these tags (``elements'' below) is \begin{verbatim}<``ELEMENT'' parameters> body of element <\``ELEMENT''>\end{verbatim} HTML has a variaty of tags for many types of environments on a webpage. There are two special tags, \verb+<div>+ and \verb+<script>+. The \verb+<script>+ is for executing JavaScript on the client-side of  a webpage. While the \verb+<div>+ tag stands for dynamic, this dynamic element usually gets its properties from a piece of JavaScript executed somewhere on the webpage which adds some dynamic content to the webpage such as user preferences, for example.
\section{JavaScript}
JQuery is a wrapper for JavaScript that simplifies the complicated UI features of JavaScript into several methods. This reduces the time it takes to code these UI effects so you can focus on writing useful code for the implementation of your website. JavaScript can be used in HTML as well as other places. These scripts are executed in the \verb+<script>+ environment of the HTML. This is used to make the pages more dynamic by storing user data such as cookies and user preferences as well as making async requests to other services, which is what we will be doing.  

\section{Conclusion}
Since we are implementing a basic UI, we will be using HTML 5 but will not be using JQuery at this time. HTML and simple JavaScript will be used for implementation of the website for the basic user interface.

\end{document}
